Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-11 paper/main.tex
product categories

We model data as the sheaf $\sheaf_{\dtotal}: \mathcal{\dbase}^{op}\rightarrow \mathcal{\dtotal}$
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheafc_{\dtotalc}", bend left] \arrow[uu, "\sheafc_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}
where the map \dfunc\ is any arbitrary function between sheafs. The sheaf $\sheaf_{\dtotal}$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf_{\mathcal{\dtotal}}|_{k}\coloneqq \lim\limits_{U\ni k} \Gamma(U, \dtotal)$ \cite{StalkSheaf2019}.

\begin{definition} 
  \label{def:category:F} 
  The fiber category $\mathcal{\dfiber}$ consists of 
  \begin{itemize}
    \item \textit{object} a single object \dtotal, where \dtotal\ can be an object of any arbitrary category $\mathcal{C}$ 
    \item \textit{morphisms} $\dfunc \in hom_{\mathcal{F}}(F,F)$
\end{definition}

The fiber space over a point is embedded in the stalk over that point $\dfiber_{k}\hookrightarrow \mathscr{F}_{k}$. The sheaf maps \dfunc\ restricted to the stalk are members of $hom_{\mathcal{F}}(F,F)$. The maps $\varphi \in Hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$ include the types of data transformations described in \autoref{sec:related-work:equivariance}. When a fiber bundle is trivial, we can dispense with localization and directly consider the fiber maps $Hom(\dfiber_{k}, \dfiber_{k})$ over a point \dbasepoint. In \autoref{sec:artist:construction}, we assume that the fiber bundles are trivial.

\note{rewrite paragraph}
The graphic category $\mathcal{\gtotalc}$ consists of the functor object $\sheaf_{\gtotalc}: \mathcal{\gbasec}^{op} \rightarrow \Gamma(\mathcal{\gbasec}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{\gbasec}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{\gbase}, \gtotal)$ is a subcatagory of \textbf{Set}.

>>>>

We model data as the sheaf $\sheafc_{\dtotalc}: \mathcal{\dbasec}^{op}\rightarrow \mathcal{\dtotalc}$
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheafc_{\dtotalc}", bend left] \arrow[uu, "\sheafc_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}
where the map \dfunc\ is any arbitrary function between sheafs. The sheaf $\sheaf_{\dtotal}$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf_{\mathcal{\dtotal}}|_{k}\coloneqq \lim\limits_{U\ni k} \Gamma(U, \dtotal)$ \cite{StalkSheaf2019}.

\begin{definition} 
  \label{def:category:F} 
  The fiber category $\mathcal{\dfiberc}$ is a product category\cite{maclaneCategoriesWorkingMathematician2013,nlab:product_category} of zero or more arbitrary categories. In the two category case, the category $\mathcal{\dfiberc}$ consists of 
  \begin{itemize}
    \item \textit{objects} ordered pairs $(x,y)$,  $x$ is an object of $\mathcal{X}$ and  $y$ is an object of $\mathcal{Y}$
    \item \textit{morphisms} ordered pairs $(f:x\rightarrow x^{\prime}, g:y\rightarrow y^{\prime})$
    \end{itemize}
The coomposition of morphisms is defined component wise by composition in $\mathcal{X}$ and $\mathcal{Y}$.ss
\end{definition}

The fiber space over a point is embedded in the stalk over that point $\dfiber_{\dbasepoint}\hookrightarrow \mathscr{\dfiber}_{\dbasepoint}$. The sheaf maps \dfunc\ restricted to the stalk are members of $hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$. The maps $\varphi \in Hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$ include the types of data transformations described in \autoref{sec:related-work:equivariance}. When a fiber bundle is trivial, we can dispense with localization and directly consider the fiber maps $Hom(\dfiber_{\dbasepoint}, \dfiber_{\dbasepoint})$ over a point \dbasepoint. In \autoref{sec:artist:construction}, we assume that the fiber bundles are trivial.

\note{rewrite paragraph}

The domain of the artist function is the space of all possible graphics. We model this space using categories that are analogous to the data categories

We model the space of all possible graphics as a sheaf $\sheafc_{\mathcal{H}}:\mathcal{S} \rightarrow \mathcal{H}$

The graphic category $\mathcal{\gtotalc}$ is analogous to the $\

consists of the functor object $\sheaf_{\gtotalc}: \mathcal{\gbasec}^{op} \rightarrow \Gamma(\mathcal{\gbasec}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{\gbasec}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{\gbase}, \gtotal)$ is a subcatagory of \textbf{Set}.
